---
title: "Regression"
author: "Aashana"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## R package that has a function for linear regression using S3 class

__linreg()__ function computes ordinary least squares. It calculates the following 

 * Regressions coefficients
 * The fitted values
 * The residuals
 * The degrees of freedom
 * The residual variance

```{r}
linreg <- function(formula, data){
  if(class(formula)=="formula")
  {
    X <- model.matrix(formula, data)
    y <- data[,all.vars(formula)[1]] #pick up independent variable
    
    #calculate regression coefficients
    regressioncoeffs <- solve(t(X) %*% X) %*% t(X) %*% y
    
    #calculate fitted values
    fittedvals <- X %*% regressioncoeffs
    
    #residuals
    residualvals <- y-fittedvals
    
    #the degree of freedom
    degreeoffree <- nrow(X)-ncol(X)
    
    #the residual variance
    residualvariance <- (t(residualvals) %*% residualvals) / degreeoffree
    
    #variance of regression coefficients
    varianceofcoeff <- diag(as.vector(residualvariance) * solve(t(X) %*% X))
    
    #t-values of each coeffcient 
    tvalues <- regressioncoeffs / sqrt(varianceofcoeff)
    
    #p-values
    pvalues <- 2*pt(abs(tvalues),degreeoffree)
    
    calculatedstatistics <- list("regressioncoeffs"=regressioncoeffs, "fittedvals"=fittedvals, "residualvals"=residualvals, "degreeoffree"=degreeoffree, "residualvariance"=residualvariance, "varianceofcoeff"=varianceofcoeff, "tvalues"=tvalues, "pvalues"=pvalues)
    class(calculatedstatistics) <- "linreg"
    return(calculatedstatistics)
  }
  else
  {
    stop("The first argument should be of type formula")
  }
}

```





Methods for the __linreg()__ class S3

```{r}
# print method for linreg
print.linreg <- function(x){
  
  cat("\nCall:\n", paste(deparse(x$call), sep = "\n", collapse = "\n"), 
      "\n\n", sep = "")
  cat("Coefficients:\n")
  print(format(t(x[["regressioncoeffs"]])[1,]), print.gap = 2L, 
        quote = FALSE)
}

# plot methd for linreg
plot.linreg <- function(x){
  
}

# resd method for linreg
resid.linreg <- function(x) {
  as.vector(x[["residualvals"]])
}

pred.linreg <- function(x) {
  x[["fittedvals"]]
}

coef.linreg <- function(x) {
  c(t(x[["regressioncoeffs"]]))
}

```



## LiU theme

There two themes for liu.

theme_liu1 has a white background for plots and has grids and axis of the liu blue
theme_liu2 has a liu blue background and has white grids and axis. With both having axis numbers or scale in liu's grey color.

Both the themes are created using ggplot2.
Custom themes can be made by passing specific arguments to the theme() function.
A general data frame of faithful and iris has been used for giving an example of how plots look like. 
```{r}

theme_liu1 <- function(){
  ggplot2::theme_bw()+
  ggplot2::theme(panel.background = ggplot2::element_rect(fill = "#FFFFFF", colour = "#666666"),
        panel.grid.major = ggplot2::element_line(colour = "#54d8e0", size=0.3),
        panel.grid.minor = ggplot2::element_line(colour = "#54d8e0", size=0.3),
        axis.line = ggplot2::element_line(size =0.3, colour = "#54d8e0"),
        axis.text = ggplot2::element_text(size = ggplot2::rel(0.8)),
        axis.ticks = ggplot2::element_line(colour = "#54d8e0"),
        legend.key = ggplot2::element_rect(colour = "#54d8e0"),
        panel.border = ggplot2::element_rect(fill = NA, colour = "#54d8e0"),
        strip.background = ggplot2::element_rect(fill = "grey80", colour = "#54d8e0"))
}

ggplot2::ggplot(faithful, ggplot2::aes(x=eruptions, y=waiting))+
  ggplot2::geom_point()+
  theme_liu1()


theme_liu2 <- function(){
  ggplot2::theme_bw()+
    ggplot2::theme(panel.background = ggplot2::element_rect(fill = "#54d8e0", colour = "#666666"),
          panel.grid.major = ggplot2::element_line(colour = "#FFFFFF", size=0.3),
          panel.grid.minor = ggplot2::element_line(colour = "#FFFFFF", size=0.3),
          axis.line = ggplot2::element_line(size =0.3, colour = "#54d8e0"),
          axis.text = ggplot2::element_text(size = ggplot2::rel(0.8)),
          axis.ticks = ggplot2::element_line(colour = "#54d8e0"),
          legend.key = ggplot2::element_rect(colour = "#54d8e0"),
          panel.border = ggplot2::element_rect(fill = NA, colour = "#54d8e0"),
          strip.background = ggplot2::element_rect(fill = "grey80", colour = "#54d8e0"))
     #annotation_custom(picc, xmin=5, xmax=7, ymin=30, ymax=45)
}

ggplot2::ggplot(iris, ggplot2::aes(x=Sepal.Length, y=Petal.Length))+
  ggplot2::geom_point()+
  theme_liu2()


# imgg <- png::readPNG("/Users/aashana/RcourseLAB4/images/liuLogo.png")
# picc <- as.raster(imgg, 10, 10, 10, 10, angle = 0, interpolate = TRUE)

```


