---
title: "Regression"
author: "Aashana"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
```{r include=FALSE}
library(RcourseLAB4)
library(ggplot2)
```

## R package that has a function for linear regression using S3 class

__linreg()__ function computes ordinary least squares. It calculates the following 

 * Regressions coefficients
 * The fitted values
 * The residuals
 * The degrees of freedom
 * The residual variance

```{r}
lm <- linreg(formula = Petal.Length ~ Species, data = iris)
```


Methods for the __linreg()__ class S3

# print method for linreg
```{r}
RcourseLAB4::print.linreg(lm)
```

# plot methd for linreg
```{r}
RcourseLAB4::plot(lm)
```

# resd method for linreg
```{r}
RcourseLAB4::resid(lm)
```

# pred method for linreg
```{r}
RcourseLAB4::pred(lm)
```

# coef method for linreg
```{r}
RcourseLAB4::coef(lm)
```

# summary method for linreg
```{r}
RcourseLAB4::summary(lm)
```



## LiU theme

There two themes for liu.

theme_liu1 has a white background for plots and has grids and axis of the liu blue
theme_liu2 has a liu blue background and has white grids and axis. With both having axis numbers or scale in liu's grey color.

Both the themes are created using ggplot2.
Custom themes can be made by passing specific arguments to the theme() function.
A general data frame of faithful and iris has been used for giving an example of how plots look like. 
```{r}
RcourseLAB4::theme_liu1()

RcourseLAB4::theme_liu2()
```


