---
title: "Regression"
author: "Aashana"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## R package that has a function for linear regression using S3 class

__linreg()__ function computes ordinary least squares. It calculates the following 

 * Regressions coefficients
 * The fitted values
 * The residuals
 * The degrees of freedom
 * The residual variance

```{r}
linreg <- function(formula, data){
  if(class(formula)=="formula")
  {
    X <- model.matrix(formula, data)
    y <- data[,all.vars(formula)[1]] #pick up independent variable
    
    #calculate regression coefficients
    regressioncoeffs <- solve(t(X) %*% X) %*% t(X) %*% y
    
    #calculate fitted values
    fittedvals <- X %*% regressioncoeffs
    
    #residuals
    residualvals <- y-fittedvals
    
    #the degree of freedom
    degreeoffree <- nrow(X)-ncol(X)
    
    #the residual variance
    residualvariance <- (t(residualvals) %*% residualvals) / degreeoffree
    
    #variance of regression coefficients
    varianceofcoeff <- diag(as.vector(residualvariance) * solve(t(X) %*% X))
    
    #t-values of each coeffcient 
    tvalues <- regressioncoeffs / sqrt(varianceofcoeff)
    
    #p-values
    pvalues <- 2*pt(abs(tvalues),degreeoffree)
    
    calculatedstatistics <- list("regressioncoeffs"=regressioncoeffs, "fittedvals"=fittedvals, "residualvals"=residualvals, "degreeoffree"=degreeoffree, "residualvariance"=residualvariance, "varianceofcoeff"=varianceofcoeff, "tvalues"=tvalues, "pvalues"=pvalues)
    class(calculatedstatistics) <- "linreg"
    return(calculatedstatistics)
  }
  else
  {
    stop("The first argument should be of type formula")
  }
}

```


## Examples

This linear regression can be performed on exisiting data like Iris and Faithful.
The following are the results

* For __IRIS__ data set

```{r}
p <- linreg(formula = Petal.Length ~ Species, data = iris)
```

* For __Faithful__ data set

```{r}
q <- linreg(formula = eruptions ~ waiting, data = faithful)
```

Methods for the __linreg()__ class S3

```{r}
# print method for linreg
print.linreg <- function(x){
  
  cat("\nCall:\n", paste(deparse(x$call), sep = "\n", collapse = "\n"), 
      "\n\n", sep = "")
  cat("Coefficients:\n")
  print(format(t(x[["regressioncoeffs"]])[1,]), print.gap = 2L, 
        quote = FALSE)
}

# plot methd for linreg
plot.linreg <- function(x){
  
}

# resd method for linreg
resid.linreg <- function(x) {
  as.vector(x[["residualvals"]])
}

pred.linreg <- function(x) {
  x[["fittedvals"]]
}

coef.linreg <- function(x) {
  c(t(x[["regressioncoeffs"]]))
}

```




